Adolescent well-being in the digital age

### 2022-03-30 00-clean.Rmd
Small fixes

# Confirm that correct measures were downloaded:
distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

>>>>

# Confirm that correct measures were downloaded:
# distinct(gbd, measure, metric)
gbd <- select(gbd, -metric, -measure)
gbd <- gbd %>%
  mutate(across(c(val, upper, lower), ~ .x / 100000))

### 2022-03-30 02-results.Rmd
Small fixes

```{r setup}
#| cache: false
# Packages
library(tidyverse)
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(memoise)
library(cachem)
library(posterior)
library(ggh4x)
library(parameters)
library(emmeans)
library(patchwork)
library(multidplyr)

@@

timecourses_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()

timecourses_world_average %>% 
  unnest(out)
```

@@

```{r}
get_region_timecourse_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note 1 for 10 year change
    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_timecourse_avg <- memoise(
  get_region_timecourse_avg, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_avg")
cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
timecourses_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_avg)) %>% 
  collect()
timecourses_region_average %>% 
  unnest(out)
```

@@

```{r}
get_region_timecourse_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note 1 for decade change
    crossing(year = c(0, 1), se = 0, itu = TRUE) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | age) + 
        (year*sex | region) + (year*sex | age:region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_timecourse_age <- memoise(
  get_region_timecourse_age, cache = cd
)

@@

internet_associations_world_average <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()

internet_associations_world_average %>% 
  unnest(out)
```

@@

```{r}
internet_associations_world_age <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
internet_associations_world_age %>% 
  unnest(out)
```

@@

cluster_copy(cluster, "get_internet_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
internet_associations_region_average <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_avg)) %>% 
  collect()
internet_associations_region_average %>% 
  unnest(out)
```

@@

cluster_copy(cluster, "get_internet_region_association_age")
internet_associations_region_age <- fits %>% 
  slice(1:3) %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_age)) %>% 
  collect()
```

@@

mobile_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()

mobile_associations_world_average %>% 
  unnest(out)
```

@@

```{r}
get_region_association_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_association_avg <- memoise(
  get_region_association_avg, cache = cd
)

cluster_copy(cluster, "get_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
mobile_associations_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_avg)) %>% 
  collect()
mobile_associations_region_average %>% 
  unnest(out)
```

@@

```{r}
get_region_association_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | age) + 
        (m1_cw*sex | region) + (m1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_association_age <- memoise(
  get_region_association_age, cache = cd
)

cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
cluster_copy(cluster, "get_region_association_age")
mobile_associations_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_age)) %>% 
  collect()
```

>>>>

```{r setup}
#| cache: false
# Packages
library(scales)
library(kableExtra)
library(ggstance)
library(brms)
library(tidybayes)
library(ggdist)
library(memoise)
library(cachem)
library(posterior)
library(ggh4x)
library(parameters)
library(emmeans)
library(patchwork)
library(multidplyr)
library(tidyverse)

@@

timecourses_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_timecourses, model = "1")
    )
  ) %>% 
  collect()
```

@@

```{r}
get_region_timecourse_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note 1 for 10 year change
    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_timecourse_avg <- memoise(
  get_region_timecourse_avg, cache = cd
)

cluster_copy(cluster, "get_region_timecourse_avg")
cluster_library(cluster, c("dplyr", "tidyr", "tidybayes"))
timecourses_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_timecourse_avg)) %>% 
  collect()
```

@@

```{r}
get_region_timecourse_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-1.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note 1 for decade change
    crossing(year = c(0, 1), se = 0, itu = TRUE, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (year*sex | age) + 
        (year*sex | region) + (year*sex | age:region),
      resp = "val",
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = year, values_from = .epred) %>% 
    mutate(delta = `1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_timecourse_age <- memoise(
  get_region_timecourse_age, cache = cd
)

@@

internet_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
```

@@

```{r}
internet_associations_world_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_age(.x, h = h_internet_associations, model = "2")
    )
  ) %>% 
  collect()
```

@@

cluster_copy(cluster, "get_internet_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
internet_associations_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_avg)) %>% 
  collect()
```

@@

cluster_copy(cluster, "get_internet_region_association_age")
internet_associations_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_internet_region_association_age)) %>% 
  collect()
```

@@

mobile_associations_world_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(
    out = map(
      outcome,
      ~get_hyp_avg(.x, h = h_mobile_associations, model = "3")
    )
  ) %>% 
  collect()
```

@@

```{r}
get_region_association_avg <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, .draw, delta) %>% 
    group_by(region, sex) %>% 
    mean_qi(delta)
}
get_region_association_avg <- memoise(
  get_region_association_avg, cache = cd
)

cluster_copy(cluster, "get_region_association_avg")
cluster_library(cluster, c("dplyr", "tidyr", "purrr", "stringr", "tidybayes"))
mobile_associations_region_average <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_avg)) %>% 
  collect()
```

@@

```{r}
get_region_association_age <- function(outcome) {
  x <- readRDS(str_glue("models/brm-{outcome}-3.rds"))
  tmp <- x$data %>% 
    distinct(region, sex, age) %>% 
    # Note .1 for 10% change
    crossing(m1_cw = c(0, .1), se = 0, year = 0, val = 1) %>% 
    add_epred_draws(
      x,
      re_formula = ~ (m1_cw*sex | age) + 
        (m1_cw*sex | region) + (m1_cw*sex | age:region),
      ndraws = 1000
    ) %>% 
    ungroup()
  tmp %>% 
    select(-.row, -se, -.chain, -.iteration, -val) %>% 
    pivot_wider(names_from = m1_cw, values_from = .epred) %>% 
    mutate(delta = `0.1` - `0`) %>% 
    select(region, sex, age, .draw, delta) %>% 
    group_by(region, sex, age) %>% 
    mean_qi(delta)
}
get_region_association_age <- memoise(
  get_region_association_age, cache = cd
)

cluster_library(cluster, c("dplyr", "tidyr", "tidybayes", "purrr"))
cluster_copy(cluster, "get_region_association_age")
mobile_associations_region_age <- fits %>% 
  group_by(outcome) %>% 
  partition(cluster) %>% 
  mutate(out = map(outcome, get_region_association_age)) %>% 
  collect()
```
